Going Beyond Ideal Point Points: Modeling Measurement Model Measurement Error

### 2023-05-23 paper.qmd
new title yay

---
title: "How to Deal With Measurement Error in Measurement Models"
author: "Bertrand Wilden"
date: "`r Sys.Date()`"
format:
  pdf:
    documentclass: article
    number-sections: true
    geometry: 
      - left=25mm
      - right=25mm
    indent: true
    fontsize: 11pt
    linestretch: 2
    fig-cap-location: top
    include-in-header:
      text:
        \usepackage{amsmath}
bibliography: [references.bib, packages.bib]
nocite : |
  @R-dplyr, @R-ggdist, @R-ggplot2, @R-ggtext, @R-MetBrewer, @R-patchwork, @R-targets, @R-cmdstanr, @R-here, @R-MCMCpack, @R-purrr, @R-readr, @R-stantargets
execute: 
  echo: false
  message: false
  warning: false
---

@@

```{r}
#| label: fig-measurement-model
#| fig-cap: "Ignoring Measurement Error in Measurement Models"
N <- 100000
tibble(x = c(rnorm(N, sd = 1.5),
             rnorm(N, sd = 4),
             sn::rsn(N, alpha = -4, omega = 4, xi = 3)),
       y = c(rep("a", N), rep("b", N), rep("c", N))) |> 
  ggplot(aes(x = x)) +
  geom_density(color = "black", fill = "darkcyan", alpha = .5) +
  facet_wrap(~ y, nrow = 1) +
  theme_void()
```

>>>>

---
title: "Going Beyond Ideal Point Points: Modeling Measurement Model Measurement Error"
author: "Bertrand Wilden"
date: "`r Sys.Date()`"
format:
  pdf:
    documentclass: article
    number-sections: true
    geometry: 
      - left=25mm
      - right=25mm
    indent: true
    fontsize: 11pt
    linestretch: 2
    fig-cap-location: top
    include-in-header:
      text:
        \usepackage{amsmath}
bibliography: [references.bib, packages.bib]
nocite : |
  @R-dplyr, @R-ggdist, @R-ggplot2, @R-ggtext, @R-MetBrewer, @R-patchwork, @R-targets, @R-cmdstanr, @R-here, @R-MCMCpack, @R-purrr, @R-readr, @R-stantargets
execute: 
  echo: false
  message: false
  warning: false
---

@@

```{r}
#| label: fig-measurement-model
#| fig-cap: "Ignoring Measurement Error in Measurement Models"
N <- 100000
tibble(x = c(rnorm(N, sd = 1),
             rnorm(N, sd = 2),
             sn::rsn(N, alpha = -4, omega = 2, xi = 1.5),
             sn::rst(N, xi = -2.75, omega = 2, alpha = 4, nu = 1)),
       y = c(rep("a", N), rep("b", N), rep("c", N), rep("d", N))) |> 
  ggplot(aes(x = x)) +
  geom_density(color = "black", fill = "darkcyan", alpha = .5) +
  facet_wrap(~ y, nrow = 2) +
  xlim(-6, 6) +
  theme_void()
```
